Local Search, Brute-Force and Recursion for Selection Operator\thanks{This work was not supported by Velbazhd Software LLC and Bulgarian Ministry of Education and Science.}

### 2020-04-11 Local-Search-Brute-Force-and-Recursion-for-Selection-Operator/paper.tex
Introduction was completed.

>>>>

The rest of the paper is organized as follows: After the introductory part proposition for local search extension to recursive brute-force selection operator is presented; Some experiments and results are presented after that; Paper concludes with a summary of the research and with some directions for a further work.

\section{Local Search Proposition}
